Taming the Bitvector Bestiary

### 2024-07-28 paper.tex
Move related work to the back
try to clarify authorship order early
Rationale: I've been in situations in the past where it's been sticky since authorship order wasn't communciated clearly.
I'd rather declare up-front what we believe the order ought to be, and discuss disagreements if they arise
(the author list I chose, is, I believe, sensible --- It will be interesting to see if this leads to disagreement!)

\documentclass[review, anonymous, sigplan]{acmart}

@@

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                      %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}
}
\email{first1.last1@inst1.edu}          %% \email is recommended

\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                      %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}
}
\email{first2.last2@inst2b.org}         %% \email is recommended

@@

\input{outline/01-introduction.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}

>>>>

% \documentclass[review, anonymous, sigplan]{acmart}
\documentclass[review, sigplan]{acmart}

@@

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.
% \author{First1 Last1}
% \authornote{with author1 note}          %% \authornote is optional;
% \orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
% \affiliation{
%   \position{Position1}
%   \department{Department1}              %% \department is recommended
%   \institution{Institution1}            %% \institution is required
%   \streetaddress{Street1 Address1}
%   \city{City1}
%   \state{State1}
%   \postcode{Post-Code1}
%   \country{Country1}
% }
% \email{first1.last1@inst1.edu}          %% \email is recommended
\author{Alex Keizer, Siddharth Bhat, Henrik B{\"o}ving, Author4, Author5, Tobias Grosser}

@@

\input{outline/01-introduction.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}
\input{outline/06-Related-Work.tex}
